Crunching Large Graphs with Commodity Processors

### 2011-03-09 doc/hotpar2011/softxmt-hotpar2011.tex
new author order

\authorinfo{Jacob Nelson, Brandon Myers, A.H. Hunter, Preston Briggs,
  Dan Grossman, Mark Oskin, Carl Ebeling, Simon Kahan, Luis
  Ceze}{University of Washington}{\{nelson, bdmyers, ahh, preston,
  djg, oskin, ebeling, skahan, luisceze\}@cs.washington.edu}

>>>>

\authorinfo{Jacob Nelson$^{\dagger}$, Brandon Myers$^{\dagger}$, A.H. Hunter$^{\dagger}$, Luis
  Ceze$^{\dagger}$,
  Dan Grossman$^{\dagger}$, Mark Oskin$^{\dagger}$, Carl Ebeling$^{\dagger}$, Simon Kahan$^{{\dagger \ddagger}}$, Preston Briggs$^{\dagger}$}{\textdagger University of Washington, \textdaggerdbl Pacific Northwest National Laboratory}{\{nelson, bdmyers, ahh, luisceze, djg, oskin, ebeling, skahan, preston\}@cs.washington.edu}
